---
title: "DDP Course Project"
author: "AAbellon1"
date: "2023-08-07"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction
The purpose of this Shiny App is to examine the relationships that may be present between each of the 4 variables found within the U.S. Arrests dataset. **In the app, the user may choose which 2 specific variables they want to examine the relationship of.** From here, a **scatterplot** of the points will be generated, along with a **trendline** and its corresponding **regression equation** which has been calculated for. 

## Overview of U.S. Arrests Dataset
The variables found in the dataset consist of the following:

```{r dataset, echo=FALSE, message=FALSE}
vars = colnames(USArrests)
```
1. **`r vars[1]`:** Murder arrests (per 100,000)
2. **`r vars[2]`:** Assault arrests (per 100,000)
3. **`r vars[3]`:** Percent urban population
4. **`r vars[4]`:** Rape arrests (per 100,000)

## Sample Insights
Examples of insights that can be gained from this Shiny App include:

* Correlation Between Assault and Murder Rates
* Urban Population and Crime Rates
* Rape and Assault Rates Analysis

## Try Out the App Here!
* The Shiny application can be accessed here: https://m1habs-michael0andre-abellon.shinyapps.io/DDP-Course-Project-App/

* The GitHub repository containing the Shiny App server and UI code can be accessed here:
https://github.com/AAbellon1/DDP-Course-Project